\plaintitle

### 2016-08-14 drafts/labor/trackingWork.tex
various additional notes and a fix with some colors and todonotes or something
moving things around

\documentclass{sigchi}

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth}
\usepackage[normalem]{ulem}
% \usepackage{url}
% \def\UrlOrds{\do\*\do\-\do\~\do\'\do\"\do\-}%
% \usepackage{multibib}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
% \usepackage{biblatex}
% \usepackage[square,numbers]{jnatbib}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\begin{document}
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\title{\plaintitle}

@@

\maketitle

\begin{abstract}
  With growing attention toward on--demand labor
  --- ranging from the ``sharing economy'' to information work ---
  scholars have made connections to various frameworks 
  and mechanisms such as worker advocacy, empowerment, and Taylorism,
  to make sense of our observations of
  on--demand work and the workers that power this movement.
  We argue that the literature surrounding ``piecework''
  informs and even predicts both the contributions
  that have been made toward the development of on--demand labor and crowd work
  as well as the fallout among workers and researchers
  with regard to the disillusionment and alienation of work.

>>>>

\documentclass[chi_draft]{sigchi}

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes}
\usepackage[normalem]{ulem}
% \usepackage{url}
% \def\UrlOrds{\do\*\do\-\do\~\do\'\do\"\do\-}%
% \usepackage{multibib}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
% \usepackage{biblatex}
% \usepackage[square,numbers]{jnatbib}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\begin{document}
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}
\title{\plaintitle}

@@

\maketitle
\begin{abstract}
  With growing attention toward on--demand labor
  --- ranging from the ``sharing economy'' to information work ---
  scholars have made connections to various frameworks 
  and mechanisms such as worker advocacy, empowerment, and Taylorism,
  to make sense of our observations of
  on--demand work and the workers that power this movement.
  We argue that the literature surrounding ``piecework''
  informs and even predicts both the contributions
  that have been made toward the development of on--demand labor and crowd work
  as well as the fallout among workers and researchers
  with regard to the disillusionment and alienation of work.
